\Large{Adversarial Training against Systematic Uncertainty}

### 2016-10-27 tex/paper.tex
fix typos

Jets, or collimated sprays of particles produced
by high energy quarks and gluons, are produced ubiqitiously at high
energy colliders like the Large Hadron Collider \citep{LHCMachine}.  In a wide
array of new physcis models, new highly massive particles can decay
though known heavy particles in Standard Model (SM), like the $W$, $Z$, Higgs bosons, or top
quarks which subsequently decay to mutiple quarks.  When these these
heavy SM particles have significant energy, the Lorentz boost causes
their quark decay products to merge into a single jet which has a rich
internal substructure (see e.g.  \citep{Altheimer:2012mn,Altheimer:2013yza} and references
therin).  Distinguishing these \textit{boosted jets} produced by heavy SM particles
from vanilla quarks and  gluons is a fundamental challenge in
searching for signs of new high mass particles.

Challenging in it's own right, this classification problem is
made all the more difficult by the presence of pileup, or multiple simultaneous
proton-proton interactions occuring at the same time as the
primary interaction.  These pileup interactions produce additional
particles that can contributie singificant energies to jets unrelated to
the underlying discrimnating information. Thus pileup acts as a source of noise in
the classification problem.

% In collisions at the Large Hadron Collider, massive particles can be produced at
% such high energies that their decay products are collimated and the resulting
% jets overlap. Still, deducing whether an observed jet is either due  to a single
% hadronic particle or to the decay of a massive object into multiple hadronic
% particles  is critical for understanding the nature of the particles produced in
% the collision \citep{butterworth2008jet,guest2016jet}. Critically, this
% classification problem is often made difficult by the presence of simultaneous
% interactions, known as pileup, which contributes significant energy depositions
% unrelated to the particles of interest.

The classification challenge used here is common in jet substructure
studies (see \citep{Khachatryan:2014vla,ATL-PHYS-PUB-2015-033,wbosonATLAS} and
references therein): we aim to discriminate between jets produced by quark or gluon fragmentation (the
background) and  boosted $W$ boson jets containing a collimated pair of
quarks (the signal).  We reuse the datasets used in reference
\citep{guest2016jet}.  Briefly summarizing, jets are built with the
anti-$k_T$ algoritm \citep{Cacciari:2008gp} 
with radius parameter $R=1.2$, and trimmed \citep{Krohn:2009th} with subjets built with
the $k_T$ algorithm and parameter $f_{cut}=0.2$. The features used
in the classifiers are: trimmed jet invariant mass, N-subjettiness
$\tau_{21}^{\beta=1}$ \citep{nsub,Thaler2012}, and the energy correlation
functions \citep{Larkoski2013} $C_{2}^{\beta=1}$, $C_{2}^{\beta=2}$,
$D_{2}^{\beta=1}$, $D_{2}^{\beta=2}$.

>>>>

Jets, or collimated sprays of particles produced by high energy quarks and
gluons, are produced ubiquitously at high energy colliders like the Large Hadron
Collider \citep{LHCMachine}.  In a wide array of new physics models, new highly
massive particles can decay though known heavy particles in Standard Model (SM),
like the $W$, $Z$, Higgs bosons, or top quarks which subsequently decay to
multiple quarks.  When these these heavy SM particles have significant energy,
the Lorentz boost causes their quark decay products to merge into a single jet
which has a rich internal substructure (see e.g.
\citep{Altheimer:2012mn,Altheimer:2013yza} and references therein).
Distinguishing these \textit{boosted jets} produced by heavy SM particles from
vanilla quarks and  gluons is a fundamental challenge in searching for signs of
new high mass particles. Challenging in it's own right, this classification
problem is made all the more difficult by the presence of pileup, or multiple
simultaneous proton-proton interactions occurring at the same time as the primary
interaction.  These pileup interactions produce additional particles that can
contribute significant energies to jets unrelated to the underlying
discriminating information. Thus pileup acts as a source of noise in the
classification problem.

The classification challenge used here is common in jet substructure
studies (see \citep{Khachatryan:2014vla,ATL-PHYS-PUB-2015-033,wbosonATLAS} and
references therein): we aim to discriminate between jets produced by quark or gluon fragmentation (the
background) and  boosted $W$ boson jets containing a collimated pair of
quarks (the signal).  We reuse the datasets used in reference
\citep{guest2016jet}.  Briefly summarizing, jets are built with the
anti-$k_T$ algorithm \citep{Cacciari:2008gp}
with radius parameter $R=1.2$, and trimmed \citep{Krohn:2009th} with subjets built with
the $k_T$ algorithm and parameter $f_{cut}=0.2$. The features used
in the classifiers are: trimmed jet invariant mass, N-subjettiness
$\tau_{21}^{\beta=1}$ \citep{nsub,Thaler2012}, and the energy correlation
functions \citep{Larkoski2013} $C_{2}^{\beta=1}$, $C_{2}^{\beta=2}$,
$D_{2}^{\beta=1}$, $D_{2}^{\beta=2}$.
